### 2019-07-01 report/chapter02.Rnw
correction of tes

#Study.year quantiles:
#data.ext2 <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), quantile(data.ext2$study.year, 0.25, na.rm = T), 
                            quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
                            round(mean(data.ext2$study.year, na.rm = T), 2))

@@

#Total and group size quantiles:
data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), quantile(data.ext2$total.n, 0.25, na.rm = T), 
                            quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
                            round(mean(data.ext2$total.n, na.rm = T), 2))
treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
                      quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
                      round(mean(data.ext2$total1, na.rm = T), 2))

#Frequencies of results:
comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
                      round(mean(comp.freq$n, na.rm = T), 2))

#Frequencies of studies:
study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
                      round(mean(study.freq$n, na.rm = T), 2))

@@

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}). The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}. Only a handful ($n = 18$) have been published in 2018, none in 2019. \\
%No information is available concerning unpublished results and studies.
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).

<<echo=FALSE, results='asis'>>=
print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
             caption = "Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,", 
             align = "llll", digits = 1), include.rownames = F, size = "footnotesize")
@

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]} and third quartile = \Sexpr{samplesize.range[4]}. The mean is \Sexpr{samplesize.range[5]}. \\
The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}. There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total. \\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous. Importantly, this distinction is also used by the Cochrane Organization itself, i.e. the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:

@@

print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
@

>>>>

#Study.year quantiles:
#data.ext2 <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), quantile(data.ext2$study.year, 0.25, na.rm = T), 
                            quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
                            round(mean(data.ext2$study.year, na.rm = T), 2), quantile(data.ext2$study.year, 0.95, na.rm = T))

@@

#Total and group size quantiles:
data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), quantile(data.ext2$total.n, 0.25, na.rm = T), 
                            quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
                            round(mean(data.ext2$total.n, na.rm = T), 2), quantile(data.ext2$total.n, 0.95, na.rm = T))
treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
                      quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
                      round(mean(data.ext2$total1, na.rm = T), 2), quantile(data.ext2$total1, 0.95, na.rm = T))

#Frequencies of results:
comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
                      round(mean(comp.freq$n, na.rm = T), 2), quantile(comp.freq$n, 0.95, na.rm = T))

#Frequencies of studies:
study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
                      round(mean(study.freq$n, na.rm = T), 2), quantile(study.freq$n, 0.95, na.rm = T))

@@

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},). The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}. Only a handful ($n = 18$) have been published in 2018, none in 2019. \\
%No information is available concerning unpublished results and studies.
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).

<<echo=FALSE, results='asis'>>=
print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
             caption = "Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,", 
             align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
@

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile and 95\% smaller than \Sexpr{treatment.group.size.range[6]}. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}. The mean is \Sexpr{samplesize.range[5]}. \\
The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}. There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous. Importantly, this distinction is also used by the Cochrane Organization itself, i.e. the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.

@@

print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials $\\geq$ n", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
@
